We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-07 paper/paper.tex
matrices
matrix
figsize

\section{Results from ELVIS and Illustris1}
\begin{figure*}
\centering
\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_width.pdf}
\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_width.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
\caption{ELVIs results for the quantities presented for the Illustris1-Dark
  simulation in Figures  \ref{fig:scatter_width},
  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
Upper row corresponds to the raw values from observations and
simulated pairs, while the second row normalizes the same values to
the mean and standard deviation on its spherically randomized
counterparts. 
\label{fig:scatter_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_M31.pdf}
\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_MW.pdf}
\caption{
Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
computed from the ELVIS data.
\label{fig:correlations_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.28\textwidth]{scatter_ranked_width.pdf}
\includegraphics[width=0.28\textwidth]{scatter_ranked_ca_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_width.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
\includegraphics[width=0.28\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
\caption{Same layout as Figure \ref{fig:scatter_elvis}, this time
  computed from the Illustris1 data.
\label{fig:scatter_illustris}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_M31.pdf}
\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_MW.pdf}
\caption{
Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
computed from the Illustris1 data.
\label{fig:correlations_illustris}}
\end{figure*}

\section{Covariance Matrices and Mean value vectors}
Illustris M31

Covariance
\begin{verbatim}
[[ 0.83+/-0.03  0.78+/-0.04  0.41+/-0.04]
 [ 0.78+/-0.04  1.16+/-0.05 -0.15+/-0.05]
 [ 0.41+/-0.04 -0.15+/-0.05  0.96+/-0.04]]
\end{verbatim}

Mean

\begin{verbatim}
[-0.18+/-0.04 -0.41+/-0.05  -0.20+/-0.05]
\end{verbatim}

Illustris MW
\begin{verbatim}
[[ 0.78+/-0.06  0.63+/-0.07  0.40+/-0.03]
 [ 0.63+/-0.07  0.69+/-0.08   0.06+/-0.02]
 [ 0.40+/-0.03  0.06+/-0.02   0.61+/-0.04]]
\end{verbatim}

Mean
\begin{verbatim}
[-0.17+/-0.04 -0.40+/-0.04 -0.23+/-0.04]
\end{verbatim}

IllustrisDM M31

Covariance
\begin{verbatim}
[[ 1.50+/-0.08  1.27+/-0.08  0.64+/-0.04]
 [ 1.27+/-0.08  1.31+/-0.08  0.28+/-0.04]
 [ 0.64+/-0.04  0.28+/-0.04  0.70+/-0.04]]
\end{verbatim}

Mean
\begin{verbatim}
[-0.37+/-0.05 -0.55+/-0.05  -0.13+/-0.03]
\end{verbatim}

IllustrisDM M31

Covariance
\begin{verbatim}
[[ 1.03+/-0.05  0.94+/-0.05  0.36+/-0.03 ]
 [ 0.94+/-0.05  1.24+/-0.07 -0.18+/-0.04]
 [ 0.36+/-0.03  -0.18+/-0.04  0.86+/0.03]]
\end{verbatim}

Mean
\begin{verbatim}
[-0.45+/-0.04 -0.61+/-0.05 -0.31+/-0.04]
\end{verbatim}

ELVIS M31

Covariance
\begin{verbatim}
[[ 1.60+/-0.19  1.22+/-0.14  0.70+/-0.09]
 [ 1.22+/-0.14  1.08+/-0.10  0.35+/-0.05]
 [ 0.70+/-0.09  0.35+/-0.05  0.63+/-0.10]]
\end{verbatim}

Mean
\begin{verbatim}
[-0.18+/-0.08 -0.28+/-0.07 -0.22+/-0.05]
\end{verbatim}

ELVIS MW
Covariance
\begin{verbatim}
[[ 0.45+/-0.04    0.61+/-0.09 -0.11+/-0.09 ]
 [ 0.61+/-0.09  1.21+/-0.17 -0.63+/-0.09]
 [-0.11+/-0.05  -0.63+/-0.09  0.64+/-0.06]]
\end{verbatim}

\begin{verbatim}
[-0.32+/-0.04 -0.74+/-0.07 -0.08+/-0.05]
\end{verbatim}

>>>>

\section{Results from ELVIS and Illustris1}
\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
\caption{ELVIs results for the quantities presented for the Illustris1-Dark
  simulation in Figures  \ref{fig:scatter_width},
  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
Upper row corresponds to the raw values from observations and
simulated pairs, while the second row normalizes the same values to
the mean and standard deviation on its spherically randomized
counterparts. 
\label{fig:scatter_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_M31.pdf}
\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_MW.pdf}
\caption{
Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
computed from the ELVIS data.
\label{fig:correlations_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_ranked_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
\caption{Same layout as Figure \ref{fig:scatter_elvis}, this time
  computed from the Illustris1 data.
\label{fig:scatter_illustris}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{gaussian_model_illustris_M31.pdf}
\includegraphics[width=0.48\textwidth]{gaussian_model_illustris_MW.pdf}
\caption{
Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
computed from the Illustris1 data.
\label{fig:correlations_illustris}}
\end{figure*}

\newpage
\newpage
\section{Covariance Matrices and Mean value vectors}
\subsection{Illustris-1}

\subsubsection{M31}

\[
\Sigma= 
\begin{bmatrix}
0.83\pm 0.03  & 0.78\pm 0.04  & 0.41\pm 0.04\\
0.78\pm 0.04  & 1.16\pm 0.05 & -0.15\pm 0.05\\
0.41\pm 0.04 & -0.15\pm 0.05 & 0.96\pm 0.04\\
\end{bmatrix}
\]

\[
\mu= 
\begin{bmatrix}
-0.18\pm 0.04 & -0.41\pm 0.05  -0.20\pm 0.05
\end{bmatrix}
\]

\subsubsection{MW}

\[
\Sigma= 
\begin{bmatrix}
 0.78\pm 0.06 & 0.63 \pm 0.07  & 0.40 \pm 0.03\\
  0.63\pm 0.07 & 0.69 \pm 0.08 &  0.06 \pm 0.02\\
  0.40\pm 0.03 & 0.06 \pm 0.02 &  0.61\pm 0.04\\
\end{bmatrix}
\]

\[
\mu= 
\begin{bmatrix}
-0.17\pm 0.04 & -0.40\pm 0.04 -0.23\pm 0.04\\
\end{bmatrix}
\]

\subsection{Illustris-1-Dark}

\subsubsection{M31}

\[
\Sigma= 
\begin{bmatrix}
 1.50\pm 0.08 & 1.27\pm 0.08 & 0.64\pm 0.04\\
  1.27\pm 0.08 &  1.31\pm 0.08&  0.28\pm 0.04\\
  0.64\pm 0.04 &  0.28\pm 0.04 & 0.70\pm 0.04\\
\end{bmatrix}
\]

\[
\mu= 
\begin{bmatrix}
-0.37\pm 0.05& -0.55\pm 0.05 & -0.13\pm 0.03\\
\end{bmatrix}
\]

\subsubsection{MW}

\[
\Sigma= 
\begin{bmatrix}
 1.03\pm 0.05 & 0.94\pm 0.05  & 0.36\pm 0.03\\
  0.94\pm 0.05 & 1.24\pm 0.07 & -0.18\pm 0.04\\
  0.36\pm 0.03 & -0.18\pm 0.04  & 0.86\pm 0.03\\
\end{bmatrix}
\]

\[
\mu= 
\begin{bmatrix}
-0.45\pm 0.04 & -0.61\pm 0.05 & -0.31\pm 0.04\\
\end{bmatrix}
\]

\subsection{ELVIS}

\subsubsection{M31}

\[
\Sigma= 
\begin{bmatrix}
 1.60\pm 0.19  & 1.22\pm 0.14 & 0.70 \pm 0.09\\
  1.22\pm 0.14 &  1.08\pm 0.10 & 0.35 \pm 0.05\\
  0.70\pm 0.09 & 0.35\pm 0.05  & 0.63 \pm 0.10\\
\end{bmatrix}
\]

\[
\mu= 
\begin{bmatrix}
-0.18\pm 0.08 & -0.28\pm 0.07 &-0.22\pm 0.05\\
\end{bmatrix}
\]

\subsubsection{MW}

\[
\Sigma= 
\begin{bmatrix}
 0.45\pm 0.04 & 0.61\pm0.09 & -0.11\pm0.09 \\
  0.61\pm0.09 & 1.21\pm0.17 & -0.63\pm0.09\\
 -0.11\pm0.05 & -0.63\pm0.09 & 0.64\pm0.06\\
\end{bmatrix}
\]

\[
\mu= 
\begin{bmatrix}
-0.32\pm 0.04 -0.74\pm 0.07 -0.08\pm 0.05\\
\end{bmatrix}
\]
